NFC and burnout in teachers - A replication and extension study

### 2021-09-24 Manuscript/Manuscript.Rmd
added plot for explor2, but it is a mess

  # Correlations show that Covid burden is positively associated with MBI and
  # and MBI_EE, and negatively associated with DTH. We will therefore include
  # Covid burden as a mediator between DTH and MBI.

@@

  # structural model
    COVB ~ YEARS
    SCS ~ YEARS
    NFC ~ SCS
    DTH ~ COVB + DRF
    DRF ~ SCS + NFC
    MBI_EE ~ DTH
    MBI_RPE ~ DRF'

@@

  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```

>>>>

@@

  # structural model
    COVB ~ YEARS
    SCS ~ YEARS
    NFC ~~ SCS
    NFC ~~ COVB
    DTH ~ COVB + SCS + NFC
    DRF ~ SCS + NFC
    DTH ~~ DRF
    MBI_EE ~ DTH + COVB
    MBI_RPE ~ DRF

    dth1 ~~ dth2
    dth1 ~~ dth3
    dth2 ~~ dth3

    drf1 ~~ drf2
    drf1 ~~ drf3
    drf2 ~~ drf3
'

@@

  fit_explor2_summ <- summary(fit_explor2, fit.measures = TRUE, standardize = TRUE, rsquare = TRUE,
          estimates = TRUE, ci = TRUE)
```
```{r explor2_plot, echo=FALSE, message=FALSE, warning=FALSE}

  fit_explor2_param <- fit_explor2_summ$PE$std.all[c(1:10,16:32)]
  fit_explor2_sign <- c(rep(1,10), fit_explor2_summ$PE$pvalue[16:32])

  fit_explor2_sign <- ifelse(fit_explor2_sign < .001, "***", ifelse(fit_explor2_sign < .01, "**", ifelse(fit_explor2_sign < .05, "*", "")))

  fit_explor2_param <- paste(format(round(fit_explor2_param, digits = 2), nsmall = 2), fit_explor2_sign, sep = "")

  fit_explor2_plot <- semPaths(fit_explor2, what = "std",
                        nodeLabels = c("nfc1","nfc2","nfc3","nfc4",
                                       "dth1","dth2","dth3","drf1","drf2","drf3",
                                       "YEARS",
                                       "SCS",
                                       "COVB",
                                       "NFC",
                                       "DRF","DTH",
                                       "MBI_EE","MBI_RPE"),
                        layout = matrix(data = c(-0.7,-0.56,-0.44,-0.3,
                                                 0.3,0.5,0.7,0.3,0.5,0.7,
                                                 -1,
                                                 -0.4,
                                                 -0.4,
                                                 -0.4,
                                                 0.4,0.4,
                                                 1,1,
                                                 1,1,1,1,
                                                 1,1,1,-1,-1,-1,
                                                 -0.3,
                                                 -1,
                                                 -0.3,
                                                 0.5,
                                                 0.5,-0.5,
                                                 0.5,-0.5),
                                        nrow = 18, ncol = 2),
                        residuals = FALSE, fade = FALSE,
                        edgeLabels = fit_explor2_param, # specify the edge labels with the asterisks as previously created
                        edge.label.cex = 1, esize = 2, # size of the parameters
                        edge.label.color = "black", edge.label.bg = TRUE, # color and background of the parameters
                        posCol = "black", negCol = "black" # color of arrows
  )
```
